\vspace{-2cm} Government websites as data: A methodological pipeline for collection, processing, and text analysis

### 2017-12-25 paper/tables/stmTopWordsLADem.tex
LA is finally working completely, results are much better

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 18:17:05 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
-0.144 & -0.077 & -0.039 & -0.02 & -0.018 & -0.015 & -0.012 & -0.011 \\ 
  \hline
stream & obj & otherwis & polic & wherea & type & communiti & art \\ 
  length & ascent & provid & crime & ordin & content & neighborhood & call \\ 
  predictor & flag & respect & investig & citi & width & citi & cost \\ 
  acrobat & descent & thereto & offic & resolut & pdf & program & sponsor \\ 
  librari & encod & author & arrest & provid & height & public & free \\ 
  pdf & interpol & citi & inform & code & filter & develop & amp \\ 
  ash & matrix & district & suspect & street & parent & opportun & music \\ 
  hum & kid & ordin & victim & shall & count & particip & artist \\ 
  gym & baa & amend & block & chapter & resourc & creat & museum \\ 
  parent & filter & locat & street & provis & size & provid & home \\ 
   \hline
\end{tabular}
\caption{Top Democratic topics and words (Louisiana), according to STM. 
             The words are the top words for the most Democratic/Republican topic, determined
             by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMLADem}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Dec 25 01:20:56 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
-0.044 & -0.04 & -0.021 & -0.019 & -0.016 & -0.012 & -0.011 & -0.01 \\ 
  \hline
owner & provide & victim & application & employee & city & revenue & community \\ 
  applicant & otherwise & crime & motion & policy & ordinance & fund & neighborhood \\ 
  new & respect & violence & second & city & whereas & tax & district \\ 
  application & thereto & arrest & street & report & bond & budget & police \\ 
  per & city & domestic & favor & department & resolution & million & public \\ 
  exist & authorize & officer & retention & audit & code & total & meeting \\ 
  build & ordinance & suspect & john & review & provide & year & engagement \\ 
  proposal & amend & report & arc & management & shall & general & crime \\ 
  receive & district & child & window & procedure & provision & service & officer \\ 
  construction & locate & police & heather & work & fund & forecast & department \\ 
   \hline
\end{tabular}
\caption{Top Democratic topics and words (Louisiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMLADem}
\end{table}

### 2017-12-25 paper/tables/stmTopWordsLARep.tex
LA is finally working completely, results are much better

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 18:17:04 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
0.085 & 0.062 & 0.062 & 0.057 & 0.021 & 0.019 & 0.018 & 0.017 \\ 
  \hline
event & ordin & citi & flood & west & properti & park & councilman \\ 
  park & bid & mayor & emerg & north & plan & street & said \\ 
  inform & summari & said & citi & east & zone & citi & citi \\ 
  food & amount & year & storm & south & lot & improv & mayor \\ 
  music & citi & state & resid & traffic & applic & recreat & want \\ 
  show & depart & announc & weather & boulevard & shall & work & council \\ 
  visit & public & work & inform & parish & requir & public & just \\ 
  market & contract & offici & hurrican & drive & approv & repair & think \\ 
  weekend & approv & resid & disast & road & use & program & vote \\ 
  begin & accord & million & power & locat & site & includ & thank \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words (Louisiana), according to STM. 
             The words are the top words for the most Democratic/Republican topic, determined
             by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMLARep}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Mon Dec 25 01:20:56 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
0.08 & 0.069 & 0.065 & 0.038 & 0.03 & 0.015 & 0.012 & 0.009 \\ 
  \hline
emergency & call & ordinance & say & say & city & home & school \\ 
  city & art & bid & city & councilman & mayor & church & program \\ 
  resident & event & city & new & mayor & council & house & youth \\ 
  weather & sponsor & summary & make & city & member & building & student \\ 
  storm & cost & authorize & work & council & board & build & recreation \\ 
  area & free & resolution & can & ordinance & commission & state & community \\ 
  official & music & amount & year & budget & director & old & child \\ 
  hurricane & show & department & take & meeting & office & first & high \\ 
  work & information & public & get & ask & district & store & city \\ 
  mayor & feature & contract & one & follow & public & one & center \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words (Louisiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMLARep}
\end{table}
